---
title: "Diferencia Medias 07.01.2022"
author: "Luca Bettini"
date: "4/1/2022"
output:
  pdf_document: default
  html_document:
    df_print: paged
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


* * * * * * * * * *

# Import libraries  
- library(dplyr)  
- library(plyr)  
- library(car)  
- library(nortest)  

```{r import, include=FALSE}
library(dplyr)
library(plyr)
library(car)
library(nortest)
```

# Import database ChildCarSeats_clean.csv
- ChildCarSeats_clean <- read.csv("ChildCarSeats_clean.csv", stringsAsFactors = TRUE)

```{r read, include=FALSE}
ChildCarSeats_clean <- read.csv("ChildCarSeats_clean.csv", stringsAsFactors = TRUE)
```

# DataBase first inspection
- str(ChildCarSeats_clean)
- summary(ChildCarSeats_clean)

```{r str, echo=TRUE}
str(ChildCarSeats_clean)
```

```{r summary, echo=TRUE}
summary(ChildCarSeats_clean)
```

# 1) Study variable Sales with US
  
Create 2 datasets settings (US_IN = 258 lines, US_OUT = 142 lines):  
- US_IN<-ChildCarSeats_clean %>% filter(US=="Yes")  
- US_OUT<-ChildCarSeats_clean %>% filter(US=="No")  

```{r varUS, include=FALSE}
#2 datasets settings
US_IN<-ChildCarSeats_clean %>%
  filter(US=="Yes")
US_OUT<-ChildCarSeats_clean %>%
  filter(US=="No")
US_IN
US_OUT
```
US_IN and US_OUT are datasets not paired. 
  
## 1.1) Study US_IN normality

```{r norm_US_IN, include=TRUE, echo=TRUE}
qqPlot(US_IN$Sales)
hist(US_IN$Sales)
###############################
shapiro.test(US_IN$Sales)
###############################
lillie.test(US_IN$Sales)
```
Both lillie (0.5236) and shapiro (0.6499) tests p_value are high so US_IN normal.  

## 1.2) Study US_OUT normality

```{r norm_US_OUT, include=TRUE, echo=TRUE}
qqPlot(US_OUT$Sales)
hist(US_OUT$Sales)
###############################
shapiro.test(US_OUT$Sales)
###############################
lillie.test(US_OUT$Sales)
```
Both lillie (0.1762) and shapiro (0.2181) tests p_value are high so US_OUT normal.  
  
## 1.3) Double check US with ddply, in order to confirm normality  
  
```{r norm_US_ddply, include=TRUE, echo=TRUE}
ddply(ChildCarSeats_clean,"US",summarise,normality_test = lillie.test(Sales))
```
The two p-values (0.5235926, 0.1761735) are the same as previous lillie test in singles datasets study; p-value are high so US normality is confirmed. 
  
## 1.4) Compare US_IN and US_OUT variances  

```{r var_US_INOUT, include=TRUE, echo=TRUE}
var.test(US_IN$Sales,US_OUT$Sales)
```
P-value (0.0008679) is low so variances are not equals
  
## 1.5) US t.test with var.equal = FALSE 
  Both US_IN and US_OUT are normal so we can perform t.test with var.equal = FALSE.

```{r t.test_US_INOUT_G, include=TRUE, echo=TRUE}
t.test(US_IN$Sales, US_OUT$Sales, paired = F ,var.equal = F, alternative = "greater")
```
Risk (that is p-value = 5.208e-07) to say US_IN are greater than US_OUT is lower than 5%.  
**Conclusion is US_IN sales are greater than US_OUT sales.**  
  
# 2) Study variable Sales with Urban 
  
Create 2 datasets settings URBAN_YES = 282 lines, URBAN_NO = 118 lines)  
- URBAN_YES<-ChildCarSeats_clean %>% filter(Urban=="Yes")  
- URBAN_NO<-ChildCarSeats_clean %>% filter(Urban=="No")  

```{r varURBAN, include=FALSE}
#2 datasets settings
URBAN_YES<-ChildCarSeats_clean %>%
  filter(Urban=="Yes")
URBAN_NO<-ChildCarSeats_clean %>%
  filter(Urban=="No")
URBAN_YES
URBAN_NO

```
URBAN_YES and URBAN_OUT are datasets not paired.  
  
## 2.1) Study URBAN_YES normality

```{r norm_URBAN_YES, include=TRUE, echo=TRUE}
qqPlot(URBAN_YES$Sales)
hist(URBAN_YES$Sales)
###############################
shapiro.test(URBAN_YES$Sales)
###############################
lillie.test(URBAN_YES$Sales)

```

Both lillie (0.2984) and shapiro (0.2993) tests p_value are high so URBAN_YES normal.  
  
## 2.2) Study URBAN_NO normality

```{r norm_URBAN_NO, include=TRUE, echo=TRUE}
qqPlot(URBAN_NO$Sales)
hist(URBAN_NO$Sales)
###############################
shapiro.test(URBAN_NO$Sales)
###############################
lillie.test(URBAN_NO$Sales)
```

Both lillie (0.7297) and shapiro (0.6306) tests p_value are high so URBAN_NO normal.  
  
## 2.3) Double check URBAN with ddply, in order to confirm normality  

```{r var_URBAN_ddply, include=TRUE, echo=TRUE}
ddply(ChildCarSeats_clean,"Urban",summarise,normality_test = lillie.test(Sales))
```
The two p-values (0.2984125, 0.7297145) are the same as previous lillie test in singles datasets study; p-value are high so URBAN normality is confirmed.   
  
## 2.4) Compare URBAN_YES and URBAN_NO variances  

```{r var_URBAN_YESNO, include=TRUE, echo=TRUE}
var.test(URBAN_YES$Sales,URBAN_NO$Sales)
```
P-value (0.9545) is high so variances are equals.  
  
## 2.5.1) URBAN t.test with var.equal = TRUE and greater
  Both URBAN_YES and URBAN_NO are normal so we can perform t.test with var.equal = TRUE and greater

```{r t.test_URBAN_YESNO_G, include=TRUE, echo=TRUE}
t.test(URBAN_YES$Sales, URBAN_NO$Sales, paired = F ,var.equal = T, alternative = "greater")
```
Risk (that is p-value = 0.6805) to say Sales of URBAN_YES are greater than Sales of URBAN_NO is 68.05%, so risk is higher than 5%.  
**Conclusion: based on 5% rule, we should refuse URBAN_YES Sales is greater than URBAN_NO.**  

## 2.5.2) URBAN t.test with var.equal = TRUE and less
  Both URBAN_YES and URBAN_NO are normal so we can perform t.test with var.equal = TRUE and less

```{r t.test_URBAN_YESNO_L, include=TRUE, echo=TRUE}
t.test(URBAN_YES$Sales, URBAN_NO$Sales, paired = F ,var.equal = T, alternative = "less")
```
Risk (that is p-value = 0.3195) to say Sales of URBAN_YES are less than Sales of URBAN_NO is 31.95%, so risk is higher than 5%.  
**Conclusion: based on 5% rule, we should refuse URBAN_YES Sales is less than URBAN_NO.**  
  
## 2.5.3) URBAN t.test with var.equal = TRUE and two.sided
  Both URBAN_YES and URBAN_NO are normal so we can perform t.test with var.equal = TRUE and two.sided

```{r t.test_URBAN_YESNO_TS, include=TRUE, echo=TRUE}
t.test(URBAN_YES$Sales, URBAN_NO$Sales, paired = F ,var.equal = T, alternative = "two.sided")
t.test(URBAN_NO$Sales, URBAN_YES$Sales, paired = F ,var.equal = T, alternative = "two.sided")
```
Risk (that is p-value =  0.639) to say Sales of URBAN_YES and URBAN_NO are two sided is 63.9%, so risk is higher than 5%.  
**Conclusion: based on 5% rule, we should refuse Sales of URBAN_YES and URBAN_NO are two sided.**  
  
# 3) Study variable Sales with ShelveLoc
  
Create 3 datasets settings SHELVELOC_GOOD = 85 lines, SHELVELOC_MEDIUM = 219 lines, SHELVELOC_BAD = 96 lines)  
- SHELVELOC_GOOD<-ChildCarSeats_clean %>% filter(ShelveLoc=="Good")  
- SHELVELOC_MEDIUM<-ChildCarSeats_clean %>% filter(ShelveLoc=="Medium")  
- SHELVELOC_BAD<-ChildCarSeats_clean %>% filter(ShelveLoc=="Bad")  

```{r varShelveLoc, include=FALSE}

#3 datasets settings
SHELVELOC_GOOD<-ChildCarSeats_clean %>%
  filter(ShelveLoc=="Good")
SHELVELOC_MEDIUM<-ChildCarSeats_clean %>%
  filter(ShelveLoc=="Medium")
SHELVELOC_BAD<-ChildCarSeats_clean %>%
  filter(ShelveLoc=="Bad")
SHELVELOC_GOOD
SHELVELOC_MEDIUM
SHELVELOC_BAD

```
SHELVELOC_GOOD and SHELVELOC_MEDIUM and SHELVELOC_BAD are datasets not paired.  
  
## 3.1) Study SHELVELOC_GOOD normality
  
```{r norm_SHELVELOC_GOOD, include=TRUE, echo=TRUE}
qqPlot(SHELVELOC_GOOD$Sales)
hist(SHELVELOC_GOOD$Sales)
###############################
shapiro.test(SHELVELOC_GOOD$Sales)
###############################
lillie.test(SHELVELOC_GOOD$Sales)
```
Both lillie (0.7634) and shapiro (0.8411) tests p_value are high so URBAN_NO normal. 
  
## 3.2) Study SHELVELOC_MEDIUM normality
  
```{r norm_SHELVELOC_MEDIUM, include=TRUE, echo=TRUE}
qqPlot(SHELVELOC_MEDIUM$Sales)
hist(SHELVELOC_MEDIUM$Sales)
shapiro.test(SHELVELOC_MEDIUM$Sales)  
###############################
lillie.test(SHELVELOC_MEDIUM$Sales)
```
Both lillie (0.633) and shapiro (0.3139) tests p_value are high so URBAN_NO normal.  
  
## 3.3) Study SHELVELOC_BAD normality
  
```{r norm_SHELVELOC_BAD, include=TRUE, echo=TRUE}
qqPlot(SHELVELOC_BAD$Sales)
hist(SHELVELOC_BAD$Sales)
###############################
shapiro.test(SHELVELOC_BAD$Sales)  
###############################
lillie.test(SHELVELOC_BAD$Sales)
```
Both lillie (0.1374) and shapiro (0.6066) tests p_value are high so URBAN_NO normal.  
  
## 3.4) Double check SHELVELOC with ddply, in order to confirm normality  

```{r var_SHELVELOC_GMB, include=TRUE, echo=TRUE}
ddply(ChildCarSeats_clean,"ShelveLoc",summarise,normality_test = lillie.test(Sales))
```
Three p-values (0.1374479, 0.7634104, 0.6329789) are the same as previous lillie test in singles datasets study; p-value are high so normality is confirmed.  
  
## 3.5) Homoscedasticity of SHELVELOC  
```{r var_SHELVELOC_HOMOSC, include=TRUE, echo=TRUE}
bartlett.test(Sales ~ ShelveLoc, data=ChildCarSeats_clean)
```
The result p-value (0.7042) is high so we do not discard equality if variances

## 3.6) Perform ANOVA TEST
```{r var_SHELVELOC_ANOVA, include=TRUE, echo=TRUE}
Result_Anova=aov(Sales ~ ShelveLoc, data=ChildCarSeats_clean)
summary(Result_Anova)
```
The result p-value (< 2e-16) is low so three means are different

## 3.7) Perform POST HOC TEST (what means are different in between)
```{r var_SHELVELOC_POSTHOC, include=TRUE, echo=TRUE}
TukeyHSD(Result_Anova)
```
The result p-value (0) is low for all cases, three means are different in between



